Global Optimization of an Analog Method by Means of Genetic Algorithms

### 2016-09-13 Genetic algorithms - MWR/template.tex
Reducing font sizes in plots.
Minor updates.

% TODO: reduce font size in plots
% TODO: AMS guidelines

@@

\begin{figure*}[t]
	\begin{center}
		\noindent\includegraphics[width=33pc,angle=0]{fig08.pdf}\\
	\end{center}
	\caption{Influence of the mutation options (section \ref{sec:gas}\ref{sec:gas:operators}\ref{sec:gas:mutation}) on the optimization performance, leaving the optimizer choose the pressure level of the atmospheric circulation analogy (single level of analogy). For the non-uniform mutation, $\omega=0.1$ in every case. The predictand is precipitation over a subcatchment in the Swiss Alps (Binn-Simplon region). The continuous bottom line represents the score of the sequential calibration and the dashed superior line, the score of the optimization without automatic selection of the pressure levels. Same conventions as Fig. \ref{fig:operator_selectcoupl_score}.}
	\label{fig:operator_mutation_score_atmlevel}
\end{figure*}

\begin{figure*}[t]
	\begin{center}
		\noindent\includegraphics[width=33pc,angle=0]{fig09.pdf}\\
	\end{center}
	\caption{Same as Fig. \ref{fig:operator_mutation_score_atmlevel}, but for another region in the Swiss Alps, with different atmospheric influences.}
	\label{fig:operator_mutation_score_rhoneamont}
\end{figure*}

@@

\begin{figure}[t]
	\begin{center}
		\noindent\includegraphics[width=11pc,angle=0]{fig14.pdf}\\
	\end{center}
	\caption{Influence of the intermediate population (IG) ratio on the optimization performance. Same conventions as Fig. \ref{fig:operator_selectcoupl_score}.}
	\label{fig:option_popratio_score}
\end{figure}

>>>>

% TODO: AMS guidelines
% TODO: compléter DOI

@@

\begin{figure*}[t]
	\begin{center}
		\noindent\includegraphics[width=33pc,angle=0]{fig08.pdf}\\
	\end{center}
	\caption{Influence of the mutation options (section \ref{sec:gas}\ref{sec:gas:operators}\ref{sec:gas:mutation}) on the optimization performance, leaving the optimizer choose the pressure level of the atmospheric circulation analogy (single level of analogy). For the non-uniform mutation, $\omega=0.1$ in every case. The continuous bottom line represents the score of the sequential calibration and the dashed superior line, the score of the optimization without automatic selection of the pressure levels. Same conventions as Fig. \ref{fig:operator_selectcoupl_score}.}
	\label{fig:operator_mutation_score_atmlevel}
\end{figure*}

\begin{figure*}[t]
	\begin{center}
		\noindent\includegraphics[width=33pc,angle=0]{fig09.pdf}\\
	\end{center}
	\caption{Same as Fig. \ref{fig:operator_mutation_score_atmlevel}, but for another region in the Swiss Alps (Swiss Chablais), with different atmospheric influences.}
	\label{fig:operator_mutation_score_rhoneamont}
\end{figure*}

@@

\begin{figure}[t]
	\begin{center}
		\noindent\includegraphics[width=11pc,angle=0]{fig14.pdf}\\
	\end{center}
	\caption{Influence of the intermediate generation (IG) ratio on the optimization performance. Same conventions as Fig. \ref{fig:operator_selectcoupl_score}.}
	\label{fig:option_popratio_score}
\end{figure}
